A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-20 manuscript.Rmd
revision

author:
  - name          : "Aaron Peikert"
    affiliation   : "1,2"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"

>>>>

author:
  - name          : "Aaron Peikert"
    affiliation   : "1,2"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,3"
    corresponding : yes
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"
